Time Series Models

### 2022-10-03 appendices/time_series_models.Rmd
correct incorrect arima spec in second document

ts_model_comparisons <- 
  series_of_interest %>% 
    group_by(country, sex, x) %>% 
    nest() %>% 
    mutate(
      arima_010 = map(data, fit_arima_model, order = c(1, 1, 0)),
      arima_110 = map(data, fit_arima_model, order = c(1, 1, 0))
    ) %>% 
  mutate(
    aicc_arima_010 = map_dbl(arima_010, ~summary(.) %>% pluck("aicc")),
    aicc_arima_110 = map_dbl(arima_110, ~summary(.) %>% pluck("aicc"))
  ) %>% 
  mutate(
    which_preferred = if_else(aicc_arima_010 < aicc_arima_110, "Random Walk", "Autocorrelated")
  )

@@

The Autocorrelated specification (ARIMA(1,1,0)) is preferred to RWD (ARIMA(0,1,0)) for all populations.

The following extracts the autocorrelation coefficients and visualises them.

>>>>

ts_model_comparisons <- 
  series_of_interest %>% 
    group_by(country, sex, x) %>% 
    nest() %>% 
    mutate(
      arima_010 = map(data, fit_arima_model, order = c(0, 1, 0)), # correct from order = c(1, 1, 0)
      arima_110 = map(data, fit_arima_model, order = c(1, 1, 0))
    ) %>% 
  mutate(
    aicc_arima_010 = map_dbl(arima_010, ~summary(.) %>% pluck("aicc")),
    aicc_arima_110 = map_dbl(arima_110, ~summary(.) %>% pluck("aicc"))
  ) %>% 
  mutate(
    which_preferred = if_else(aicc_arima_010 < aicc_arima_110, "Random Walk", "Autocorrelated")
  )

@@

For females, the Random Walk with Drift (RWD, ARIMA(0, 1, 0)) specification is preferred for all populations considered except Scottish and German females from age 65.

For males, the Autocorrelated specification (ARIMA(1, 1, 0)) is preferred for all populations for changes in life expectancy from birth (x = 0), whereas from age 65 the RWD specification is preferred for Spain, France, Italy,  and Scotland. 
The following extracts the autocorrelation coefficients and visualises them.
